Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2018-08-18 workflow/workflow.Rmd
rm berkeley affiliation

  - name: Fanny Perraudeau
    affiliation: 
      - Graduate Group in Biostatistics, University of California, Berkeley, Berkeley, CA
      - Whole Biome, Inc., San Francisco, CA
  - name: Davide Risso
    affiliation: Division of Biostatistics and Epidemiology, Department of Healthcare Policy and Research, Weill Cornell Medicine, New York, NY
  - name: Kelly Street
    affiliation: Graduate Group in Biostatistics, University of California, Berkeley, Berkeley, CA
  - name: Elizabeth Purdom
    affiliation: Department of Statistics, University of California, Berkeley, Berkeley, CA
  - name: Sandrine Dudoit
    affiliation: Division of Biostatistics and Department of Statistics, University of California, Berkeley, Berkeley, CA
abstract: Novel single-cell transcriptome sequencing assays allow researchers to measure gene expression levels at the resolution of single cells and offer the unprecendented opportunity to investigate at the molecular level fundamental biological questions such as stem cell differentiation or the discovery and characterization of rare cell types. However, such assays raise challenging statistical and computational questions and require the development of novel methodology and software. Using stem cell differentiation in the mouse olfactory epithelium as a case study, this integrated workflow provides a step-by-step tutorial to the methodology and associated software for the following four main tasks:(1) dimensionality reduction accounting for zero inflation and over-dispersion and adjusting for gene and cell-level covariates; (2) cell clustering using resampling-based sequential ensemble clustering; (3) inference of cell lineages and pseudotimes; and (4) differential expression analysis along lineages. 
keywords: single-cell, RNA-seq, normalization, dimensionality reduction, clustering, lineage inference, differential expression, workflow
bibliography: ref.bib
vignette: >
    %\VignetteIndexEntry{A worfklow for low-level analyses of scRNA-seq data}
    %\VignetteEngine{knitr::rmarkdown}
output: BiocWorkflowTools::f1000_article
editor_options: 
  chunk_output_type: console
---

>>>>

  - name: Fanny Perraudeau
    affiliation: 
      - Whole Biome, Inc., San Francisco, CA
  - name: Davide Risso
    affiliation: Division of Biostatistics and Epidemiology, Department of Healthcare Policy and Research, Weill Cornell Medicine, New York, NY
  - name: Kelly Street
    affiliation: Graduate Group in Biostatistics, University of California, Berkeley, Berkeley, CA
  - name: Elizabeth Purdom
    affiliation: Department of Statistics, University of California, Berkeley, Berkeley, CA
  - name: Sandrine Dudoit
    affiliation: Division of Biostatistics and Department of Statistics, University of California, Berkeley, Berkeley, CA
abstract: Novel single-cell transcriptome sequencing assays allow researchers to measure gene expression levels at the resolution of single cells and offer the unprecendented opportunity to investigate at the molecular level fundamental biological questions such as stem cell differentiation or the discovery and characterization of rare cell types. However, such assays raise challenging statistical and computational questions and require the development of novel methodology and software. Using stem cell differentiation in the mouse olfactory epithelium as a case study, this integrated workflow provides a step-by-step tutorial to the methodology and associated software for the following four main tasks:(1) dimensionality reduction accounting for zero inflation and over-dispersion and adjusting for gene and cell-level covariates; (2) cell clustering using resampling-based sequential ensemble clustering; (3) inference of cell lineages and pseudotimes; and (4) differential expression analysis along lineages. 
keywords: single-cell, RNA-seq, normalization, dimensionality reduction, clustering, lineage inference, differential expression, workflow
bibliography: ref.bib
vignette: >
    %\VignetteIndexEntry{A worfklow for low-level analyses of scRNA-seq data}
    %\VignetteEngine{knitr::rmarkdown}
output: BiocWorkflowTools::f1000_article
editor_options: 
  chunk_output_type: console
---
